The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum

### 2013-12-09 floats/figures.tex
Update location map
Add geographical names and update colormap.
Address editor comment on figures

% fig:locmap
\begin{figure}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=8cm]{cordillera-climate-locmap}
	\end{center}
	\caption{Shaded relief map of northern North America with the extent of the Cordilleran (CIS), Laurentide (LIS) and Innuitian (IIS) ice sheets at 14\,$^{14}$C\,ka\,BP (16.8\,cal\,ka\,BP) \citep{dyke-2004}. While this age denotes the LIS after retreat from its LGM, it closely corresponds to the LGM extent of most of the Cordilleran ice sheet \citep{porter-swanson-1998,dyke-2004,stroeven-etal-2010}. The rectangular box denotes the modelling domain of the Cordilleran ice sheet of 1500 by 3000\,km. The background map consists of ETOPO1 \citep{data:etopo1} and Natural Earth Data \citep{data:naturalearth} and was assembled with GRASS~GIS \citep{soft:grass}.}
	\label{fig:locmap}
\end{figure}

@@

% fig:extent
\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics{cordillera-climate-extent}
	\end{center}
	\caption{Extent of ice cover after 10\,ka as a function of applied temperature offsets for each climate forcing used.}
	\label{fig:extent}
\end{figure*}

>>>>

% fig:locmap
\begin{figure}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics[width=8cm]{cordillera-climate-locmap}
	\end{center}
	\caption{Shaded relief map of northern North America with the extent of the Cordilleran (CIS), Laurentide (LIS) and Innuitian (IIS) ice sheets at 14\,$^{14}$C\,ka\,BP (16.8\,cal\,ka\,BP) \citep{dyke-2004}. While this age denotes the LIS after retreat from its LGM, it closely corresponds to the LGM extent of most of the Cordilleran ice sheet \citep{porter-swanson-1998,dyke-2004,stroeven-etal-2010}. The rectangular box denotes the modelling domain of the Cordilleran ice sheet of 1500 by 3000\,km. Major mountain ranges covered by the ice sheet include the Wrangell and St.-Elias mountains (W-SE), the Selwyn and MacKenzie mountains (S-MK), the Coast Mountains and the Rocky Mountains. The background map consists of ETOPO1 \citep{data:etopo1} and Natural Earth Data \citep{data:naturalearth} and was assembled with GRASS~GIS \citep{soft:grass}.}
	\label{fig:locmap}
\end{figure}

@@

% fig:extent
\begin{figure*}[t]
	\vspace*{2mm}
	\begin{center}
		\includegraphics{cordillera-climate-extent}
	\end{center}
	\caption{Extent of ice cover after 10\,ka as a function of applied temperature offsets for each climate forcing used. A reconstructed LGM ice sheet margin by \citet{dyke-2004} (Fig.~\ref{fig:locmap}) is given for reference (black line).}
	\label{fig:extent}
\end{figure*}

### 2013-12-09 reviews/initial-response.tex
Address editor comment on figures

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}
%\usepackage{enumitem}
%\usepackage{letterbib}

\newcommand{\rev}[0]{\color{blue!50!black}\it}
\newcommand{\textrev}[1]{{\rev``#1''}}
\newcommand{\revpoint}[1]{{\rev\item``#1''}}
\newcommand{\todo}[1]{\textcolor{red!50!black}{Todo: #1}}
\newcommand{\done}[1]{\textcolor{green!50!black}{Done: #1}}

@@

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{graphicx}
%\usepackage{enumitem}
%\usepackage{letterbib}
\graphicspath{{../figures/}}

\newcommand{\unit}[1]{\ensuremath{\mathrm{#1}}}
\newcommand{\degree}[0]{\ensuremath{^{\circ}}}
\newcommand{\rev}[0]{\color{blue!50!black}\it}
\newcommand{\textrev}[1]{{\rev``#1''}}
\newcommand{\revpoint}[1]{{\rev\item``#1''}}
\newcommand{\todo}[1]{\textcolor{red!50!black}{Todo: #1}}
\newcommand{\done}[1]{\textcolor{green!50!black}{Done: #1}}

@@

The LGM ice margin reconstruction visible on Figs.~1 and~15 was added to Fig.~6, which shows the extent of modelled ice cover for each climate forcing used. However we did not add it to Figs.~7 and 13 as we felt the resulting figures contained too much information (Fig.~a).

@@

\begin{center}
	\includegraphics{cordillera-climate-cool05+lgm.pdf}\\
	\textbf{Fig. a.} Paper figure~7 with added LGM ice margin, not included in the new version.
\end{center}
